Reconstructing Propositional Proofs in Type Theory

### 2017-11-16 paper/sections/proof-reconstruction/clausify.tex
Cosmetic changes.
[ paper ] clausify: fixed parenthesis.
[ paper ] clausify: removed CNF abbrev.
[ slides ] lots of changes.

The \clausify rule transforms a formula into its clausal normal form.
It is important to notice that this kind of conversion between one formula
to its clausal normal form is not unique, and \Metis has a customized
approach to perform that transformation. That is the reason we perform some
reordering for the \CNF of the source formula to fulfill this issue.

\begin{myexamplenum}
In the following \TSTP derivation by \Metis, we see how
\clausify transform the \texttt{norm0} formula to get \texttt{norm1} formula.

@@

\begin{mainth}
\label{thm:clausify}
  If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \fclausify~φ~ψ$, where,

  \begin{equation*}
  \begin{aligned}
  &\hspace{.495mm}\fclausify : \Source → \Target → \Prop\\
  &\begin{array}{llll}
  \fclausify~φ~ψ &=
         \begin{cases}
        ψ, &\text{ if }φ≡ψ;\\
        \freorder_{∧∨}~(\fcnf~φ~ψ), &\text{ otherwise.}
      \end{cases}
  \end{array}
  \end{aligned}
  \end{equation*}
\end{mainth}

>>>>

The \clausify rule transforms a formula into its clausal normal form.
It is important to notice that this kind of conversion between one formula
to its clausal normal form is not unique, and \Metis has a customized
approach to perform that transformation. Hence, we perform a
reordering of the conjunctive normal form for the source formula.

\begin{myexamplenum}
In the following \TSTP derivation by \Metis, we see how
\clausify transforms the \texttt{norm0} formula to get \texttt{norm1} formula.

@@

\begin{mainth}
\label{thm:clausify}
   Let $ψ : \Target$. If $Γ ⊢ φ$ then $Γ ⊢ \fclausify~φ~ψ$, where
  \begin{equation*}
  \begin{aligned}
  &\hspace{.495mm}\fclausify : \Source → \Target → \Prop\\
  &\begin{array}{llll}
  \fclausify~φ~ψ &=
         \begin{cases}
        ψ, &\text{ if }φ≡ψ;\\
        \freorder_{∧∨}~(\fcnf~φ)~ψ, &\text{ otherwise.}
      \end{cases}
  \end{array}
  \end{aligned}
  \end{equation*}
\end{mainth}
